

\bibitem{zhai2025vlacritic}
Zhai S, Zhang Q, Zhang T, Huang F, Zhang H, Zhou M, Zhang S, Liu L, Lin S, Pang J.
A Vision-Language-Action-Critic Model for Robotic Real-World Reinforcement Learning[OL].
arXiv preprint arXiv:2509.15937, 2025.

\bibitem{abdelkareem2022advances}
Abdelkareem Y, Shehata S, Karray F.
Advances in Preference-based Reinforcement Learning: A Review[C].
2022 IEEE International Conference on Systems, Man, and Cybernetics (SMC), 2022: 2527--2532.

\bibitem{muller2025improving}
Müller H, Kudenko D.
Improving the Effectiveness of Potential-Based Reward Shaping in Reinforcement Learning[C].
Proceedings of the 24th International Conference on Autonomous Agents and Multiagent Systems (AAMAS), 2025: 2684--2686.

\bibitem{trajectory2024comparativelanguage}
Author list to verify.
Trajectory Improvement and Reward Learning from Comparative Language Feedback[OL].
arXiv preprint arXiv:2410.06401, 2024.

\bibitem{christiano2017deep}
Christiano P F, Leike J, Brown T B, Martic M, Legg S, Amodei D.
Deep Reinforcement Learning from Human Preferences[C].
Advances in Neural Information Processing Systems, 2017, 30.

\bibitem{brown2019extrapolating}
Brown D S, Goo W, Nagarajan P, Niekum S.
Extrapolating Beyond Suboptimal Demonstrations via Inverse Reinforcement Learning from Observations[C].
Proceedings of the 36th International Conference on Machine Learning (ICML), 2019: 783--792.

\bibitem{lee2021bpref}
Lee K, Smith L M, Dragan A, Abbeel P.
B-Pref: Benchmarking Preference-Based Reinforcement Learning[C].
Advances in Neural Information Processing Systems, 2021, 34.

\bibitem{prefmmt2025}
Author list to verify.
PrefMMT: Modeling Human Preferences in Preference-based Reinforcement Learning with Multimodal Transformers[OL].
arXiv preprint, 2025.

\bibitem{robodopamine2025}
Author list to verify.
Robo-Dopamine: General Process Reward Modeling for High-Precision Robotic Manipulation[OL].
arXiv preprint, 2025.

\bibitem{park2022surf}
Park J, Seo Y, Shin J.
SURF: Semi-Supervised Reward Learning with Data Augmentation for Feedback-Efficient Preference-Based Reinforcement Learning[C].
International Conference on Learning Representations (ICLR), 2022.

\bibitem{robometer2026}
Author list to verify.
Robometer: Scaling General-Purpose Robotic Reward Models via Trajectory Comparisons[OL].
arXiv preprint arXiv:2603.02115, 2026.

\bibitem{roboreward2026}
Author list to verify.
RoboReward: General-Purpose Vision-Language Reward Models for Robotics[OL].
arXiv preprint arXiv:2601.00675, 2026.

\bibitem{krack2026rewarding}
Krack P, Jülg T, Burgard W, Walter F.
Rewarding DINO: Predicting Dense Rewards with Vision Foundation Models[OL].
arXiv preprint arXiv:2603.16978, 2026.

\bibitem{ng1999policy}
Ng A Y, Harada D, Russell S.
Policy Invariance Under Reward Transformations: Theory and Application to Reward Shaping[C].
Proceedings of the 16th International Conference on Machine Learning (ICML), 1999: 278--287.

\bibitem{fu2018airl}
Fu J, Luo K, Levine S.
Learning Robust Rewards with Adversarial Inverse Reinforcement Learning[C].
International Conference on Learning Representations (ICLR), 2018.

\bibitem{ibarz2018reward}
Ibarz B, Leike J, Pohlen T, Irving G, Legg S, Amodei D.
Reward Learning from Human Preferences and Demonstrations in Atari[C].
Advances in Neural Information Processing Systems, 2018, 31.

\bibitem{lee2021pebble}
Lee K, Smith L M, Dragan A, Abbeel P.
PEBBLE: Feedback-Efficient Interactive Reinforcement Learning via Relabeling Experience and Unsupervised Pre-training[C].
Proceedings of the 38th International Conference on Machine Learning (ICML), 2021.

\bibitem{kumar2020d4rl}
Kumar A, Zhou A, Tucker G, Levine S.
D4RL: Datasets for Deep Data-Driven Reinforcement Learning[OL].
arXiv preprint arXiv:2004.07219, 2020.

\bibitem{yu2020metaworld}
Yu T, Quillen D, He Z, Julian R, Narayan A, Shively H, Bellathur A, Hausman K, Finn C, Levine S.
Meta-World: A Benchmark and Evaluation for Multi-Task and Meta Reinforcement Learning[C].
Conference on Robot Learning (CoRL), 2019.

\bibitem{radford2021clip}
Radford A, Kim J W, Hallacy C, Ramesh A, Goh G, Agarwal S, Sastry G, Askell A, Mishkin P, Clark J, Krueger G, Sutskever I.
Learning Transferable Visual Models From Natural Language Supervision[C].
Proceedings of the 38th International Conference on Machine Learning (ICML), 2021.

\bibitem{nair2022r3m}
Nair S, Rajeswaran A, Kumar V, Finn C, Gupta A.
R3M: A Universal Visual Representation for Robot Manipulation[C].
Conference on Robot Learning (CoRL), 2022.

\bibitem{ma2023vip}
Ma Y J, Sodhani S, Jayaraman D, Bastani O, Kumar V, Zhang A.
VIP: Towards Universal Visual Reward and Representation via Value-Implicit Pre-Training[C].
International Conference on Learning Representations (ICLR), 2023.

\bibitem{ma2023liv}
Ma Y J, Kumar V, Zhang A, Bastani O, Jayaraman D.
LIV: Language-Image Representations and Rewards for Robotic Control[OL].
arXiv preprint arXiv:2306.00958, 2023.

\bibitem{sontakke2023roboclip}
Sontakke S, Zhang J, Arnold J, Pertsch K, Bıyık E, Finn C, Itti L.
RoboCLIP: One Demonstration is Enough to Learn Robot Policies[OL].
arXiv preprint arXiv:2310.07899, 2023.

\bibitem{ma2024eureka}
Ma Y J, Liang W, Wang G, Huang D A, Bastani O, Jayaraman D, Zhu Y, Fan L, Anandkumar A.
Eureka: Human-Level Reward Design via Coding Large Language Models[C].
International Conference on Learning Representations (ICLR), 2024.

\bibitem{ouyang2022training}
Ouyang L, Wu J, Jiang X, Almeida D, Wainwright C L, Mishkin P, Zhang C, Agarwal S, Slama K, Ray A, Schulman J, Hilton J, Kelton F, Miller L, Simens M, Askell A, Welinder P, Christiano P, Leike J, Lowe R.
Training Language Models to Follow Instructions with Human Feedback[C].
Advances in Neural Information Processing Systems, 2022, 35: 27730--27744.

\bibitem{oquab2024dinov2}
Oquab M, Darcet T, Moutakanni T, Vo H, Szafraniec M, Khalidov V, Fernandez P, Haziza D, Massa F, El-Nouby A, Howes R, Huang P Y, Xu H, Sharma V, Li S W, Galuba W, Rabbat M, Assran M, Ballas N, Synnaeve G, Misra I, Jegou H, Mairal J, Labatut P, Joulin A, Bojanowski P.
DINOv2: Learning Robust Visual Features without Supervision[OL].
arXiv preprint arXiv:2304.07193, 2023.

\bibitem{ibarz2018reward}
Ibarz J, Leike J, Pohlen T, Irving G, Legg S, Amodei D.
Reward learning from human preferences and demonstrations in Atari[C].
Advances in Neural Information Processing Systems, 2018, 31.

\bibitem{lee2021pebble}
Lee K, Smith L M, Abbeel P.
PEBBLE: Feedback-efficient interactive reinforcement learning via relabeling experience and unsupervised pre-training[C].
Proceedings of the 38th International Conference on Machine Learning, 2021: 6152--6163.

\bibitem{liang2022rune}
Liang X, Shu K, Lee K, Abbeel P.
Reward uncertainty for exploration in preference-based reinforcement learning[J].
arXiv preprint arXiv:2205.12401, 2022.

\bibitem{ho2016gail}
Ho J, Ermon S.
Generative adversarial imitation learning[C].
Advances in Neural Information Processing Systems, 2016, 29.

\bibitem{fu2018airl}
Fu J, Luo K, Levine S.
Learning robust rewards with adversarial inverse reinforcement learning[C].
International Conference on Learning Representations, 2018.

\bibitem{finn2016guided}
Finn C, Levine S, Abbeel P.
Guided cost learning: Deep inverse optimal control via policy optimization[C].
Proceedings of the 33rd International Conference on Machine Learning, 2016: 49--58.

\bibitem{ziebart2008maximum}
Ziebart B D, Maas A L, Bagnell J A, Dey A K.
Maximum entropy inverse reinforcement learning[C].
Proceedings of the AAAI Conference on Artificial Intelligence, 2008, 8: 1433--1438.

\bibitem{reddy2020sqil}
Reddy S, Dragan A D, Levine S.
SQIL: Imitation learning via reinforcement learning with sparse rewards[C].
International Conference on Learning Representations, 2020.

\bibitem{rajeswaran2018dapg}
Rajeswaran A, Kumar V, Gupta A, Vezzani G, Schulman J, Todorov E, Levine S.
Learning complex dexterous manipulation with deep reinforcement learning and demonstrations[C].
Robotics: Science and Systems, 2018.

\bibitem{nair2022r3m}
Nair S, Rajeswaran A, Kumar V, Finn C, Gupta A.
R3M: A universal visual representation for robot manipulation[C].
Conference on Robot Learning, 2022.

\bibitem{ma2023vip}
Ma Y J, Sodhani S, Jayaraman D, Bastani O, Kumar V, Zhang A.
VIP: Towards universal visual reward and representation via value-implicit pre-training[C].
International Conference on Learning Representations, 2023.

\bibitem{liang2023liv}
Liang W, Ma Y J, Wang G, Huang D A, Bastani O, Jayaraman D.
LIV: Language-image representations and rewards for robotic control[C].
Conference on Robot Learning, 2023.

\bibitem{sontakke2023roboclip}
Sontakke S A, Zhang J, Arnold S M R, Pertsch K, Biyik E, Sadigh D, Finn C, Itti L.
RoboCLIP: One demonstration is enough to learn robot policies[C].
Advances in Neural Information Processing Systems, 2023, 36.

\bibitem{ma2024eureka}
Ma Y J, Liang W, Wang G, Huang D A, Bastani O, Jayaraman D, Zhu Y, Fan L, Anandkumar A.
Eureka: Human-level reward design via coding large language models[C].
International Conference on Learning Representations, 2024.

\bibitem{shridhar2022cliport}
Shridhar M, Manuelli L, Fox D.
CLIPort: What and where pathways for robotic manipulation[C].
Conference on Robot Learning, 2022.

\bibitem{mandlekar2021robomimic}
Mandlekar A, Xu D, Wong J, Nasiriany S, Wang C, Kulkarni R, Fei-Fei L, Savarese S, Zhu Y, Martin-Martin R.
What matters in learning from offline human demonstrations for robot manipulation[C].
Conference on Robot Learning, 2021.

\bibitem{mandlekar2023mimicgen}
Mandlekar A, Nasiriany S, Wen B, Akinola I, Narang Y S, Fan L, Zhu Y, Fox D.
MimicGen: A data generation system for scalable robot learning using human demonstrations[C].
Conference on Robot Learning, 2023.

\bibitem{zhu2020robosuite}
Zhu Y, Wong J, Mandlekar A, Martin-Martin R, Joshi A, Lin K, Maddukuri A, Nasiriany S, Zhu Y.
robosuite: A modular simulation framework and benchmark for robot learning[J].
arXiv preprint arXiv:2009.12293, 2020.

\bibitem{liu2023libero}
Liu B, Zhu Y, Gao C, Feng Y, Liu Q, Zhu Y, Stone P.
LIBERO: Benchmarking knowledge transfer for lifelong robot learning[J].
arXiv preprint arXiv:2306.03310, 2023.